% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Work Experience at the top
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Mar 22 - present}   {Senior Ruby Engineer}{Nzero}{remote}
    {} {
        \begin{itemize}
          \item Re-architected a large section of the etl pipeline to improve performance and improve data integrity.
          \item Lead a team to build an internal tool to help the  customer support team be more effective.
          \item Architected a database subseting system that allowed team members to develop locally with realistic data.
        \end{itemize}
      }
      {Ruby, Rails, Sidekiq Pro, Postgres, CircleCi}
  \emptySeparator
  \experience
    {Mar 21 - Jan 22}   {Senior Ruby Engineer}{Jane}{Vancouver British Columbia}
    {} {
        \begin{itemize}
          \item Re-architected the export system to be multi-treaded and fault tolerant. 
          \item Implemented a more robust versioning system to ensure the client code was compatible with the server.
          \item Architected a new patient experience mobile app to be iterative and scalable.
          \item Worked with the insurance team to ship several large features.
          \item Found a bug in one of or slowest endpoints that was causing a 100x slowdown.
        \end{itemize}
      }
      {Ruby, Rails, Sidekiq Pro, Postgres, CircleCi}
  \emptySeparator
  \experience
    {Oct 19- Feb 21} {Senior Fullstack Engineer}{Mavenlink}{Salt Lake City Utah}
    {Aug 17 - Oct 18} {
                      \begin{itemize}
                        \item Nearly every line of code wrote at Mavenlink was paired on and test driven.
                        \item Re-built the integrations system from a fragile hand coded prototype to a robust user extensible platform.
                        \item Ported an auxiliary service from heroku to Kubernetes.
                        \item Architected and lead a team to implement a user configurable roll rased access management system. 
                        \item Implemented a statistical testing system that would alert developers of failure rate changes.
                        \item Optional git push hook that would merge master into your development brach if master had diverged.
                      \end{itemize}
                    }
                    {Ruby, Rails, CircleCi, Elixir, React, Redux, JavaScript, Postgres, Backbone, jQuery, Kubernetes, Helm, AWS, Gcloud, Swagger, GraphQl, Pair Programing}
  \emptySeparator
  \experience
    {Nov 18 - Sept 19} {Senior Software Engineer/Team Lead}{Recursion Pharmaceuticals}{Salt Lake City Utah}
    {}    {
                      \begin{itemize}
                        \item Compound management system migration:
                        When I took over as team lead, my team was tasked with a large scale project that was already 2 quarters over due. I worked with program and product management to identify MVP and facilitated team brainstorm sessions for a robust company wide migration plan. Together we were able to finish the system in four weeks and successfully roll it out to the company.
                        \item Implemented a weekly pairing session that has helped to take the team from individually responsible for pieces of the app, to shared ownership.
                        \item Implemented a bot that integrated github to our project management tool to allow for seamless velocity tracking and task management.
                        \item Added a universal UI for internal developer documentation that was quickly adopted.
                      \end{itemize}
                    }
                    {Python, Flask, GoLang, Kafka, Postgres, React, Redux, Swagger, Docker}
  \emptySeparator
  \experience
  {Jun 15 - Jul 17}  {Software Engineer}{PassiveLogic}{Salt Lake City Utah}
  {}  {PassiveLogic is a small startup creating a revolutionary new AI driven, simulation based, building automaton system. I built the majority of the initial Client side application.}
      {EnyoJs, Swift}
  \emptySeparator
\end{experiences}
